Proof-Reconstruction in Type Theory for Propositional Logic

### 2017-10-22 paper/main.tex
added text.
[ paper ] perliminaries added.
[ paper ] implementation added, some proofs added.
[ paper ] fixing some typos and text added.
[ paper ] complexity measure added.
[ paper ] thm-split added.
[ paper ] improving minor texts.
[ paper ] Added temporally `hyperref` package.
[ paper ] citation using natbib.
[ travis-ci ] fixed cpphs requirement.
[ paper ] working.
[ paper ] cosmetics for cases equations.
[ paper ] normalization, first part, added.
[ paper ] canonicalize lemmas and theorems.
[ paper ] metis section fixes.
[ paper ] fixed athena process description.
[ paper ] first descript

\documentclass[runningheads, a4paper]{llncs}
\usepackage{subfiles}

\setcounter{tocdepth}{5}
\usepackage{graphicx}
\usepackage{array}
\usepackage{bussproofs}
\newenvironment{bprooftree}
  {\leavevmode\hbox\bgroup}
  {\DisplayProof\egroup}
\def\extraVskip{3pt}
\def\labelSpacing{3pt}
\def\defaultHypSeparation{\hskip.2in}
\def\EnableBpAbbreviations{true}

@@

@@

\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows}
\usetikzlibrary{calc}
\usepackage{rotating}

@@

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{ucs}
\usepackage{autofe}
\usepackage{afterpage}
\usepackage{comment}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsmath}
%\usepackage{stmaryrd} %new symbol font for tcs
\usepackage{color}
\usepackage{fancybox}

\usepackage{textcomp}
\usepackage[verbose]{newunicodechar}
\newunicodechar{∧}{\ensuremath{\wedge}}
\newunicodechar{∨}{\ensuremath{\vee}}
\newunicodechar{¬}{\ensuremath{\neg}}
\newunicodechar{⇒}{\ensuremath{\Rightarrow}}
\newunicodechar{⇔}{\ensuremath{\Leftrightarrow}}
\newunicodechar{∼}{\ensuremath{\sim}}
\newunicodechar{₀}{\ensuremath{{}_{0}}}
\newunicodechar{₁}{\ensuremath{{}_{1}}}
\newunicodechar{₃}{\ensuremath{{}_{2}}}
\newunicodechar{₄}{\ensuremath{{}_{3}}}
\newunicodechar{₅}{\ensuremath{{}_{4}}}
\newunicodechar{₆}{\ensuremath{{}_{5}}}
\newunicodechar{₇}{\ensuremath{{}_{6}}}
\newunicodechar{₈}{\ensuremath{{}_{7}}}
\newunicodechar{₉}{\ensuremath{{}_{8}}}
\newunicodechar{∅}{\ensuremath{\emptyset}}
\newunicodechar{⊢}{\ensuremath{\vdash}}
\newunicodechar{⊥}{\ensuremath{\bot}}
\newunicodechar{Γ}{\ensuremath{\Gamma}}

%\DeclareUnicodeCharacter{00A0}{~}

@@

% -------------------------------------------------------------------
% New commands
% -------------------------------------------------------------------
\usepackage{xspace}

\newcommand{\abbre}[1]{\textsc{#1}\xspace}
\newcommand{\ATP}{\abbre{ATP}}
\newcommand{\ATPs}{\abbre{ATPs}}
\newcommand{\SAT}{\abbre{SAT}}
\newcommand{\SMT}{\abbre{SMT}}
\newcommand{\ITP}{\abbre{ITP}}
\newcommand{\CPL}{\abbre{CPL}}
\newcommand{\CNF}{\abbre{CNF}}

@@

\newcommand{\prg}[1]{\texttt{#1}\xspace}
\newcommand{\Agda}{\prg{Agda}}
\newcommand{\Metis}{\prg{Metis}}
\newcommand{\Athena}{\prg{Athena}}
\newcommand{\IsabelleHOL}{\prg{IsabelleHOL}}

@@

@@

@@

\title{Towards Proof-Reconstruction of Problems
in Classical Propositional Logic}

\titlerunning{Proof-Reconstruction in Classical
Propositional Logic}

\author{Jonathan Prieto-Cubides%
\and Andr\'es Sicard-Ram\'irez}
%
\authorrunning{Proof-Reconstruction in Classical Propositional Logic}

\institute{Logic and Computation Research Group,\\
Universidad EAFIT, Medell\'in, Colombia\\
\email{\{jprieto9,asr\}@eafit.edu.co}}

@@

\listoftodos[Notes]

@@

\subfile{sections/abstract.tex}
\subfile{sections/introduction.tex}
\subfile{sections/metis-language-and-proofs.tex}
\subfile{sections/proof-reconstruction.tex}
\subfile{sections/conclusions.tex}
\subfile{sections/related-work.tex}
\subfile{sections/acknowledgements.tex}

\bibliographystyle{splncs03}
\bibliography{ref}
\addcontentsline{toc}{section}{References}

>>>>

\documentclass[
    envcountsect    %% In order to provide the usual behaviour expected
                    %% from \newtheorem
  , runningheads
  ]{llncs}

\spnewtheorem{mainth}[theorem]{Main Theorem}{\bfseries}{\rmfamily}

\usepackage[numbers]{natbib}

\usepackage{subfiles}

\usepackage{needspace}  %% https://tex.stackexchange.com/questions/28203/
                        %% thmtools-how-to-prevent-pagebreak-between-theorem-
                        %% and-proof

\setcounter{tocdepth}{5}
\usepackage{graphicx}
\usepackage{array}

\usepackage{bussproofs}
\newenvironment{bprooftree}
  {\leavevmode\hbox\bgroup}
  {\DisplayProof\egroup}

\def\extraVskip{3pt}
\def\labelSpacing{3pt}
\def\defaultHypSeparation{\hskip.2in}
\def\EnableBpAbbreviations{true}

@@

\usepackage{hyphenat}
\hyphenation{proof-re-cons-truc-tion proof-ob-ject}

@@

\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows}
\usetikzlibrary{calc}
\usetikzlibrary{shapes}
\usepackage{rotating}

@@

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{ucs}
\usepackage{autofe}
\usepackage{afterpage}
\usepackage{comment}
\usepackage[hyphens]{url}
\usepackage{bm}

\usepackage{amssymb}
\usepackage{amsmath}

\let\proof\relax      %% https://tex.stackexchange.com/questions/43835/
\let\endproof\relax   %% conflict-between-amsthm-and-some-other-package
\usepackage{amsthm}

\newenvironment{sketchproof}{%
  \renewcommand{\proofname}{Sketch of the Proof}\proof}{\endproof}
\renewcommand\qedsymbol{$\blacksquare$}

%\usepackage{stmaryrd} %new symbol font for tcs
\usepackage{color}
\usepackage{fancybox}

% -------------------------------------------------------------------
% Unicode Characters.
% -------------------------------------------------------------------

\usepackage{textcomp}
\usepackage[verbose]{newunicodechar}

\newunicodechar{¬}{\ensuremath{\neg}\;}
\newunicodechar{Γ}{\ensuremath{\Gamma}}
\newunicodechar{γ}{\ensuremath{\gamma}}
\newunicodechar{φ}{\ensuremath{\varphi}}
\newunicodechar{ψ}{\ensuremath{\psi}}
\newunicodechar{ϕ}{\ensuremath{\varphi}}
\newunicodechar{ᵢ}{\ensuremath{{}_{i}}}
\newunicodechar{₀}{\ensuremath{{}_{0}}}
\newunicodechar{₁}{\ensuremath{{}_{1}}}
\newunicodechar{₂}{\ensuremath{{}_{2}}}
\newunicodechar{₃}{\ensuremath{{}_{3}}}
\newunicodechar{₄}{\ensuremath{{}_{4}}}
\newunicodechar{₅}{\ensuremath{{}_{5}}}
\newunicodechar{₆}{\ensuremath{{}_{6}}}
\newunicodechar{₇}{\ensuremath{{}_{7}}}
\newunicodechar{₈}{\ensuremath{{}_{8}}}
\newunicodechar{₉}{\ensuremath{{}_{9}}}
\newunicodechar{ₙ}{\ensuremath{{}_{n}}}
\newunicodechar{→}{\ensuremath{\rightarrow}}
\newunicodechar{⇒}{\ensuremath{\Rightarrow}}
\newunicodechar{⇔}{\ensuremath{\Leftrightarrow}}
\newunicodechar{∅}{\ensuremath{\emptyset}}
\newunicodechar{∈}{\ensuremath{\in}}
\newunicodechar{∘}{\ensuremath{\circ}}
\newunicodechar{∧}{\ensuremath{\wedge}}
\newunicodechar{∨}{\ensuremath{\vee}}
\newunicodechar{∼}{\ensuremath{\sim}}
\newunicodechar{≠}{\ensuremath{\neq}}
\newunicodechar{≡}{\ensuremath{\equiv}}
\newunicodechar{⊕}{\ensuremath{\oplus}}
\newunicodechar{⊖}{\ensuremath{\ominus}}
\newunicodechar{⊢}{\ensuremath{\vdash}}
\newunicodechar{⊤}{\ensuremath{\top}}
\newunicodechar{⊥}{\ensuremath{\bot}}
\newunicodechar{⊻}{\ensuremath{\veebar}}
\newunicodechar{⟝}{\ensuremath{\vdash_{2}}}
\newunicodechar{ⱼ}{\ensuremath{{}_{j}}}

% -------------------------------------------------------------------
% Verbatim.
% -------------------------------------------------------------------

@@

% -------------------------------------------------------------------
% New commands
% -------------------------------------------------------------------

\usepackage{xspace}

\newcommand{\abbre}[1]{\textsc{#1}\xspace}
\newcommand{\ATPs}{\abbre{ATPs}}
\newcommand{\ATP}{\abbre{ATP}}
\newcommand{\Bool}{\abbre{Bool}}
\newcommand{\CNF}{\abbre{CNF}}
\newcommand{\CPL}{\abbre{CPL}}
\newcommand{\ITP}{\abbre{ITP}}
\newcommand{\ITPs}{\abbre{ITPs}}
\newcommand{\List}{\abbre{List}}
\newcommand{\NProp}{\abbre{NProp}}
\newcommand{\Nat}{\abbre{Nat}}
\newcommand{\Prop}{\abbre{Prop}}
\newcommand{\SAT}{\abbre{SAT}}
\newcommand{\SMT}{\abbre{SMT}}

@@

\newcommand{\zero}{\rm{zero}\xspace}
\newcommand{\suc}{\rm{succ}\xspace}

\newcommand{\nnf}{\name{nnf}}

\newcommand{\prg}[1]{\texttt{#1}\xspace}
\newcommand{\Agda}{\prg{Agda}}
\newcommand{\Athena}{\prg{Athena}}
\newcommand{\IsabelleHOL}{\prg{IsabelleHOL}}
\newcommand{\Metis}{\prg{Metis}}

@@

\newcommand{\NN}{\ensuremath{\mathbb{N}}}

\newcommand{\fun}[1]{\rm{#1}\xspace}
\newcommand{\fbuild}{\fun{build}}
\newcommand{\fcanon}{\fun{canon}}
\newcommand{\fcnf}{\fun{cnf}}
\newcommand{\fdist}{\fun{dist}}
\newcommand{\ffactor}{\fun{factor}}
\newcommand{\fform}{\fun{form}}
\newcommand{\fmax}{\fun{max}}
\newcommand{\fndisj}{\fun{ndisj}}
\newcommand{\fnnf}{\fun{nnf}}
\newcommand{\frank}{\fun{rank}}
\newcommand{\frconj}{\fun{rconj}}
\newcommand{\frdisj}{\fun{rdisj}}
\newcommand{\freorder}{\fun{reorder}}
\newcommand{\frm}{\fun{rm}}
\newcommand{\fsbuild}{\fun{sbuild}}
\newcommand{\fsubst}{\fun{subst}}
\newcommand{\fuh}{\fun{uh}}
\newcommand{\tunshunt}{\fun{thm-uh}}

\newcommand{\fstrip}{\fun{strip}}
\newcommand{\tstrip}{\fun{thm-strip}}

\newcommand{\fcanonicalize}{\fun{canonicalize}}
\newcommand{\tcanonicalize}{\fun{thm-canonicalize}}

\newcommand{\fconjunct}{\fun{conjunct}}
\newcommand{\tconjunct}{\fun{thm-conjunct}}

\newcommand{\fresolve}{\fun{resolve}}
\newcommand{\tresolve}{\fun{thm-resolve}}

\newcommand{\fclausify}{\fun{clausify}}
\newcommand{\tclausify}{\fun{thm-clausify}}

\newcommand{\fsimplify}{\fun{simplify}}
\newcommand{\tsimplify}{\fun{thm-simplify}}

\newcommand{\fnegate}{\fun{negate}}
\newcommand{\tnegate}{\fun{thm-negate}}

% latin etc. abbrev
\newcommand{\abbrev}[1]{#1} % alternative: \emph{#1}
\newcommand{\cf}{\abbrev{cf.}\ }
\newcommand{\eg}{\abbrev{e.\,g.}}
\newcommand{\Eg}{\abbrev{E.\,g.}}
\newcommand{\ie}{\abbrev{i.\,e.}}
\newcommand{\Ie}{\abbrev{I.\,e.}}
\newcommand{\etal}{\abbrev{et.\,al.}}
\newcommand{\wwlog}{w.\,l.\,o.\,g.} % \wlog is ``write into log file''
\newcommand{\Wlog}{W.\,l.\,o.\,g.}
\newcommand{\wrt}{w.\,r.\,t.}

@@

% -------------------------------------------------------------------
% Hyperef.
% -------------------------------------------------------------------

\usepackage{hyperref}

@@

\title{Proof-Reconstruction in Type Theory for Propositional Logic}
\author{Jonathan Prieto-Cubides%
%\and Andr\'es Sicard-Ram\'irez
}
%

\institute{Logic and Computation Research Group,\\
Universidad EAFIT, Medell\'in, Colombia\\
\email{jprieto9@eafit.edu.co}}

@@

% \listoftodos[Notes]

@@

\subfile{sections/abstract.tex}
% \tableofcontents
\subfile{sections/introduction.tex}
% \subfile{sections/preliminaries.tex}
\subfile{sections/metis-language-and-proofs.tex}
\subfile{sections/proof-reconstruction.tex}
% \subfile{sections/implementation.tex}
\subfile{sections/related-work.tex}
\subfile{sections/conclusions.tex}
\subfile{sections/acknowledgements.tex}

\bibliographystyle{plainnat}
\bibliography{ref}
\addcontentsline{toc}{section}{References}

### 2017-10-22 paper/sections/acknowledgements.tex
Last changes in the Paper (#37)
* minor changes.

* [ paper ] section 2 improvements.

* [ paper ] major changes, abstract, conclusions was added.

* [ paper ] minor changes, title and abstract.

* [ paper ] fixing some mistakes.

* [ paper ] fixing error grammars and adding notes.

* [ paper ] section 3 introduction added.

* [ paper ] appendix added.

* added text.

* [ paper ] perliminaries added.

* [ paper ] implementation added, some proofs added.

* [ paper ] fixing some typos and text added.

* [ paper ] fixing some typos and text added.

* [ paper ] complexity measure added.

* [ pape

Last but not least, we thankfully acknowledge
Andreas Abel and Chalmers University of Goteborg, Sweden for
inviting us to be part of the \Agda Implementors’ Meeting XXV.
I was honored to present there part of this research.

>>>>

Last but not least, I thankfully acknowledge
Andreas Abel and Chalmers University of Goteborg, Sweden for
inviting me to be part of the \Agda Implementors’ Meeting XXV.
I was honored to present there part of this research.

### 2017-10-22 paper/sections/related-work.tex
Last changes in the Paper (#37)
* minor changes.

* [ paper ] section 2 improvements.

* [ paper ] major changes, abstract, conclusions was added.

* [ paper ] minor changes, title and abstract.

* [ paper ] fixing some mistakes.

* [ paper ] fixing error grammars and adding notes.

* [ paper ] section 3 introduction added.

* [ paper ] appendix added.

* added text.

* [ paper ] perliminaries added.

* [ paper ] implementation added, some proofs added.

* [ paper ] fixing some typos and text added.

* [ paper ] fixing some typos and text added.

* [ paper ] complexity measure added.

* [ pape

>>>>

% On the one hand, we have the
% automatic theorem provers (henceforth \ATP) and their specification
% logic. These tools are usually classified in at least one of the
% following categories.
% A \SAT solver (e.g., \name{zChaff}~\cite{Moskewicz2001} and
% \name{MiniSat}~\cite{Een2004}) to prove unsatisfiability of \CNF
% formulas, a \abbre{QBF} solver (e.g.,
% \name{GhostQ}~\cite{Klieber2014} and
% \name{DepQBF}~\cite{Lonsing2017}) to prove satisfiability and
% invalidity of quantified Boolean formulas, a \SMT solver
% (e.g \name{CVC4}~\cite{Barrett2011}, \name{veriT}~\cite{bouton2009},
% and \name{Z3}~\cite{DeMoura2008}) to prove unsatisfiability of
% formulas from first-order logic with theories, and a prover for
% validity of formulas from first-order logic with equality
% (e.g., \name{E}~\cite{Schulz:AICOM-2002},
% \name{leanCoP}~\cite{Otten2008},
% \Metis~\cite{hurd2003first},
% \name{SPASS}~\cite{Weidenbach2009} and
% \name{Vampire}~\cite{Riazanov1999}), high-order logic (e.g.,
% \name{Leo-II}~\cite{Benzmuller2008} and
% \name{Satallax}~\cite{Brown2012}) or intuitionistic logic (e.g.,
% \name{ileanCoP}~\cite{Otten2008},
% \name{JProver}~\cite{Schmitt2001}, and
% \name{Gandalf}~\cite{Tammet1997}), among others. On the other hand,
% we have the proof checkers, interactive theorem provers (henceforth
% \ITP) or proof assistants (e.g., \Agda~\cite{agdateam},
% \name{Coq}~\cite{coqteam},
% \name{Isabelle}~\cite{paulson1994isabelle}, and
% \name{HOL4}~\cite{norrish2007hol}).

\name{Isabelle/HOL} incorporated \Metis as a macro-step
reconstruction tool for explaining proof steps (usually \CNF goals)
replied from other \ATPs like \name{CVC4}, \name{Vampire}, or
\name{Z3} (more details in Ref.~\cite{paulson2007source}).
\citeauthor{Farber2015} in \cite{Farber2015} present tactic based on \Metis for
\name{HOL Light} capable to challenge others tactics like \emph{MESON}
or the \emph{leanCoP} tactic~\cite{Farber2016}.
